Cognitive and Auditory Predictors of Dysarthric Speech Understanding in Older

### 2023-12-21 Manuscript Analyses/manuscript_analysis.Rmd
writing model functions - wip

# Loading in needed packages
library(tidyverse) #install.packages("tidyverse")
library(rio) #install.packages("rio")
library(gt) #install.packages("gt")
library(gtsummary) #install.packages("gtsummary")
library(reshape2) #install.packages("reshape2")
library(ggcorrplot) #install.packages("ggcorrplot")
library(patchwork) #install.packages("patchwork")
library(janitor) #install.packages("janitor")
library(fs) #install.packages("fs")
library(furniture) #install.packages("furniture")
library(caret) #install.packages("caret")
library(effectsize) #install.packages("effectsize")
library(parameters) #install.packages("parameters")
library(performance) #install.packages("performance")
library(bayestestR) #install.packages("bayestestR)
library(rstanarm) #install.packages("rstanarm")

@@

@@

>>>>

# Loading in needed packages
library(tidyverse) #install.packages("tidyverse")
library(rio) #install.packages("rio")
library(gt) #install.packages("gt")
library(gtsummary) #install.packages("gtsummary")
library(reshape2) #install.packages("reshape2")
library(ggcorrplot) #install.packages("ggcorrplot")
library(patchwork) #install.packages("patchwork")
library(janitor) #install.packages("janitor")
library(fs) #install.packages("fs")
library(furniture) #install.packages("furniture")
library(caret) #install.packages("caret")
library(effectsize) #install.packages("effectsize")
library(parameters) #install.packages("parameters")
library(performance) #install.packages("performance")
library(bayestestR) #install.packages("bayestestR)
library(rstanarm) #install.packages("rstanarm")
library(afex) #install.packages("afex")

@@

## Plot importance function
plot_importance = function(mods, labels){
  map2(mods, labels, ~var_imp(.x, .y)) %>% 
    reduce(full_join, by = "var") %>% 
    ungroup() %>% 
    pivot_longer(-var) %>% 
    group_by(var) %>% 
    mutate(avg_imp = mean(value, na.rm=TRUE)) %>% 
    ungroup() %>% 
    arrange(avg_imp) %>% 
    mutate(var = fct_inorder(var))
}

@@

### Pretest - Posttest Plot

pl_int %>%
  ggplot() +
  aes(x = type,
      y = mean_pwc,
      group = id) +
  geom_line(alpha = 0.3) +
  stat_summary(aes(group = speaker),
               fun.y = mean, geom = "line", linewidth = 2) +
  facet_wrap("speaker") +
  labs(x = "Phase", y = "Intelligibility") +
  theme_bw() +
  theme(legend.position = "none", aspect.ratio = 1)

# Results

## Correlations

### AM1

cor_df <- pl_int %>%
  tidyr::pivot_wider(names_from = type,
                     values_from = mean_pwc) %>%
  dplyr::mutate(improvement = posttest - pretest) %>%
  dplyr::select(id, speaker, ends_with("_c"), best_win, pretest, posttest, improvement)

AM1_cor <- cor_df %>%
  dplyr::filter(speaker == "AM1") %>%
  dplyr::select(!c(id, speaker, fluid_cog_c, posttest)) %>%
  dplyr::rename(
    `Working Memory` = list_sort_c,
    `Inhibitory Control` = flanker_c,
    `Cognitive Flexibility` = card_sort_c,
    `Receptive Vocabulary` = vocab_c,
    `Processing Speed` = pattern_c,
    `Picture Sequence Memory` = pic_seq_c,
    `Words in Noise Threshold` = best_win
  ) %>%
  dplyr::rename_all(snakecase::to_title_case) %>%
  cor(use = "pairwise.complete.obs") %>%
  ggcorrplot(
    type = "lower",
    outline.col = "white",
    colors = c("#6D9EC1", "white", "#E46726"),
    lab = TRUE,
    insig = "blank",
    title = "Ataxic", 
    legend.title = "Correlation"
  )

AM1_cor

### PDM10

PDM10_cor <- cor_df %>%
  dplyr::filter(speaker == "PDM10") %>%
  dplyr::select(!c(id, speaker, fluid_cog_c, posttest)) %>%
  dplyr::rename(
    `Working Memory` = list_sort_c,
    `Inhibitory Control` = flanker_c,
    `Cognitive Flexibility` = card_sort_c,
    `Receptive Vocabulary` = vocab_c,
    `Processing Speed` = pattern_c,
    `Picture Sequence Memory` = pic_seq_c,
    `Words in Noise Threshold` = best_win
  ) %>%
  dplyr::rename_all(snakecase::to_title_case) %>%
  cor(use = "pairwise.complete.obs") %>%
  ggcorrplot(
    type = "lower",
    outline.col = "white",
    colors = c("#6D9EC1", "white", "#E46726"),
    lab = TRUE,
    insig = "blank",
    title = "Parkinson's Disease", 
    legend.title = "Correlation"
  )

PDM10_cor

library(patchwork)
AM1_cor + PDM10_cor + plot_layout(guides = "collect") & theme(legend.position = "bottom")
ggsave("Plots/cor_fig.png", width = 20, height = 6, dpi = 300, units = "in")

## Pre-Post Change

cor_df %>% 
  dplyr::select(id, speaker, pretest, posttest) %>% 
  tidyr::pivot_longer(pretest:posttest) %>% 
  dplyr::group_by(speaker) %>% 
  dplyr::group_nest() %>% 
  dplyr::mutate(
    mod = map(data, ~afex::aov_4(value ~ 1 + (name|id), data = .x))
  ) %>% 
  pull(mod)

cor_df %>% 
  dplyr::select(id, speaker, pretest, posttest) %>% 
  tidyr::pivot_longer(pretest:posttest) %>% 
  dplyr::group_by(speaker) %>% 
  dplyr::group_nest() %>% 
  dplyr::mutate(
    mod = map(data, ~effectsize::cohens_d(value ~ name, data = .x))
  ) %>% 
  pull(mod)

## Models of Initial Intelligibility

### Cognition
